Discrete Quantum Theories and Computing

### 2018-12-04 dissertation.tex
prop.bib @InBook{Gisin2017} Added...

There was a long history that human believe they can compute with
the continuum of real numbers. If the length of a line segment represents
a real number, Euclid thought he could use an unmarked ruler and a
compass to compute the real numbers about 300 B.C~\cite{MCC2006}.
After logarithm was discovered, a slide rule, also known as a slipstick,
is used to compute multiplication, division, and more complex operations
as a mechanical analog computer~\cite{wiki:SlideRule}. Although
more and more complex analog computers, like integrators \cite{wiki:Integrator,wiki:ChargeAmplifier},
is used, there is still a gap between the computation preformed in
an analog computer and the idealized operations among real numbers.
One problem is that the quality computed by an analog computer might
actually be quantized. For example, charge amplifier is believed to
produce the integrated value of the input current~\cite{wiki:ChargeAmplifier}
although the input charge must actually be an integer multiple of
the elementary charge~\cite{wiki:ElementaryCharge}. Even for the
qualities which doesn't known to be quantized, the observed computational
power of an analog computer might still be weaker than the theoretical
prediction because the precision of an analog computer is limited
generally three or four significant figures~\cite{wiki:AnalogComputer}.
For example, Blum, Cucker, Shub, and Smale modeled their machine to
allow the operations of deciding whether a number is greater or equal
to zero over real numbers and whether a number is exactly zero over
complex numbers \cite{BSS1989,Ziegler2007,blum2012complexity}. Since
no physical analog computer could branch in these operations based
on a few significant figures, the theoretical prediction of Blum-Cucker-Shub-Smale
(BCSS) machine cannot fully apply on physical devices.

>>>>

There was a long history that human believe they can compute with
the continuum of real numbers. If the length of a line segment represents
a real number, Euclid thought he could use an unmarked ruler and a
compass to compute the real numbers about 300 B.C~\cite{MCC2006}.
After logarithm was discovered, a slide rule, also known as a slipstick,
is used to compute multiplication, division, and more complex operations
as a mechanical analog computer~\cite{wiki:SlideRule}. Although
more and more complex analog computers, like integrators \cite{wiki:Integrator,wiki:ChargeAmplifier},
is used, there is still a gap between the computation preformed in
an analog computer and the idealized operations among real numbers.
One problem is that the quality computed by an analog computer might
actually be quantized. For example, charge amplifier is believed to
produce the integrated value of the input current~\cite{wiki:ChargeAmplifier}
although the input charge must actually be an integer multiple of
the elementary charge~\cite{wiki:ElementaryCharge}. Even for the
qualities which doesn't known to be quantized, the observed computational
power of an analog computer might still be weaker than the theoretical
prediction because the precision of an analog computer is limited
generally three or four significant figures~\cite{wiki:AnalogComputer}.
\todo{See if we can cite this paper~\cite{Gisin2017} for finite
precision measurement. }For example, Blum, Cucker, Shub, and Smale
modeled their machine to allow the operations of deciding whether
a number is greater or equal to zero over real numbers and whether
a number is exactly zero over complex numbers \cite{BSS1989,Ziegler2007,blum2012complexity}.
Since no physical analog computer could branch in these operations
based on a few significant figures, the theoretical prediction of
Blum-Cucker-Shub-Smale (BCSS) machine cannot fully apply on physical
devices.
